# Absorbance {#absorbance}

## What is CDOM?

Chromophoric fraction of the DOM pool (CDOM) is a major driver of underwater light characteristics (Kirk1994) which modulate many bio-optical processes such as primary production (Thrane2014, Seekell2015) and also constitute a natural screen protecting aquatic organisms against harmful ultraviolet (UV) radiations (Boily2012). Because of its colored nature, CDOM is known to strongly absorbs UV light.

@Blough2002 provide a good definition of what is CDOM.

> Over the past decade, there has been a renewed interest in the properties and distribution of the major light-absorbing constituent of the (DOM) pool in natural waters (the 0.2 $μ$m fraction). This material—referred in the past by various names such as Gelbstoff, yellow substance, gilvin, and humic substances) has more recently been provided the name chromophoric dissolved organic matter (CDOM).

- Measured in quartz cuvette (1, 5, 10+ cm)


As wavelengths increase, light absorbed by CDOM decrease exponentially \@ref(fig:absorbance).

```{r absorbance, fig.cap = "Example of an absorption spectrum of CDOM."}

library(cdom)
data(spectra)

spectra <- spectra %>% filter(wavelength <= 500)

p <- ggplot(spectra, aes(x = wavelength, y = spc1)) +
  geom_line() +
  xlab("Wavelength (nm.)") +
  ylab(bquote(Absorption~(nm^{-1})))

p
```

## Writing and notation

In reference to this fraction of the DOM pool, people have been using interchangeably different terminology. For example, a_g($\lambda$), a($\lambda$), CDOM($\lambda$), aCDOM($\lambda$) and $a_{CDOM}(\lambda)$ are all referring to the absorption coefficient measured at wavelength $\lambda$ (nm).

To unify the terminology, we propose that absorption of CDOM should be written as $\mathbf{a_{\text{CDOM}}(\lambda)}$ using the followings *rules*:

1. *a* in *italic* to reference to absorption (vs absorbance).
2. CDOM subscript and in capital letters.
3. $\lambda$ sign to refer to the wavelength where the measurement is done.

For example, $a_{\text{CDOM}}(350)$ refers to absorption coefficient measured at 350 nm.

## Absorption vs absorbance

It is of interest to review the [Beer-Lambert law](http://www.chemguide.co.uk/analysis/uvvisible/beerlambert.html) to understand the difference between absrobance and absorption.

\begin{alignat}{2}
\label{eq:abs1}
    I_n &= I_0 \times e^{(\epsilon \times c \times L)}\\
\end{alignat}

where:

- $I_0$ the intensity of *emitted* light (before it passes through the sample).
- $I_n$ the intensity of *received* light (after it passes through the sample).
- $\epsilon$: the molar absorption coefficient ($m^2 \times \text{mole}^{-1}$).
- $c$: the concentration of the colored material in the solution ($\text{mole} \times m^{-3}$).
- $L$: the pathlenght traveled by the light throught the solution. It is of a common usage to express it per meter ($m^{-1}$).

\begin{alignat}{2}
\label{eq:abs2}
    I_n &= I_0 \times e^{-(a \times L)}\\
\end{alignat}

where $a = \epsilon \times c$ is the absorption coefficient ($m^{-1}$).

\begin{alignat}{2}
\label{eq:abs3}
    \frac{I_n}{I_0}       &= e^{-(a \times L)}\\[10pt]
    \frac{I_0}{I_n}       &= e^{(a \times L)}\\[10pt]
    log(\frac{I_0}{I_n})  &= a \times L\\[10pt]
    a                     &= \frac{log(\frac{I_0}{I_n})}{L}\\
\end{alignat}

We notice here that the Beer-Lambert law is written in log base $e$. However, for historical reasons (basically because it was esier to calculate in the *old* days), spectrophotometer use log base 10 than rather than $e$. To convert from base 10 logarithm to a natural logarithm (i.e. base $e$), one need to use the conversion factor calculated as $log(10)$ which is equato to `r log(10)`.  Then, the equation becomes:

\begin{alignat}{2}
\label{eq:abs4}
    a &= \frac{log(\frac{I_0}{I_n}) \times 2.303}{L}\\
\end{alignat}

Note that *absorbance* measured by spectrophotometers is noted $A$. Finally, 

\begin{equation}

a = \frac{A \times 2.303}{L}
\label{eq:absorption1}

\end{equation}

Because we are specifially measuring absorption of CDOM, often at a specific wavelenght $\lambda$, the recommended writing is as follow:

\begin{equation}

a_{\text{CDOM}}(\lambda) = \frac{A(\lambda) \times 2.303}{L}
\label{eq:absorption2}

\end{equation}


Where $A(\lambda)$ is the measured **absorbance** and $L$ the measurement cuvette thickness (or pathlenght) expressed per meter ($m^{-1}$).

## Mathematical formulation of absorption spectra

As observed in figure \@ref(fig:absorbance), absorption decrease exponentially with increasing wavelengths. @Jerlov1968 and @Bricaud1981 first proposed to use a simple exponential formulation to model absorption (equation \@ref(eq:cdom1)).

\begin{equation}
a_{\text{CDOM}}(\lambda) = a_{\text{CDOM}}(\lambda0)e^{-S(\lambda - \lambda0)}
\label{eq:cdom1}
\end{equation}

Where $a_{\text{CDOM}}(\lambda)$ is the absorption coefficient (m$^{-1}$), $\lambda$ is the wavelength (nm), $\lambda0$ is a reference wavelength (nm) and $S$ is the spectral slope (nm$^{-1}$) that describes the approximate exponential rate of decrease of absorption with increasing wavelength. Higher slopes indicate a more rapid decrease in absorption with increasing wavelength. The $S$ parameter is frequently used as a proxy for tracing photochemical and microbial-induced changes of CDOM [Moran2000,Twardowski2004,Helms2013] or to determine its origin [Stedmon2001].

In 2001, equation \@ref(eq:cdom1) was modified by @Stedmon2001 which introduced $k$, a background constant (m$^{-1}$) accounting for scatter in the cuvette and drift of the instrument (equation \@ref(eq:cdom2)).

\begin{equation}
a_{\text{CDOM}}(\lambda) = a_{\text{CDOM}}(\lambda0)e^{-S(\lambda - \lambda0)} + \mathbf{k}
\label{eq:cdom2}
\end{equation}

There are other mathematical formulations that can be used to model CDOM spectra. These are reviewed in @Twardowski2004.

## Modeling CDOM absorption spectra in R {#sl}

Because of it inverse exponential shape, absorption spectra are best modeled using non-linear fittings. In R this is done easy using the `nls()` function. As we can see from equation \@ref(eq:cdom2), the most commonly equation used to model CDOM spectra contains three parameters: `a0, s, k`.


```{r}
mod <- nls(spc1 ~ a0 * exp(-s * (wavelength - 250)) + k, # define the formula
           data = spectra, # where the data comes from
           start = list(a0 = 5, s = 0.02, k = 0)) # initial guesses.

# show the summary information
summary(mod)
```

The value of $a0$ is `r round(coef(mod)[1], digits = 2)` represent the absorption coefficient at the reference wavelength of 250 nm (Fig. \@ref(fig:model)). The value of $S$ is `r round(coef(mod)[2], digits = 2)` means that absorption is decreasing at a rate of `r round(coef(mod)[2], digits = 2)` $m^{-1}$ for each increase of 1 nm.

- k parameter (scattering, introduced by @Stedmon2001)

```{r model, fig.cap="Predicted values of the exponential model."}
p + geom_line(aes(y = predict(mod)), col = "red") +
  geom_hline(yintercept = coef(mod)[1] + coef(mod)[3], lty = 2) +
  geom_vline(xintercept = 250, lty = 2)

```

### Potential drawbacks

When modeling CDOM spectra, there are few things to keep in minds that can have a significant influence on model results.

#### Choice of the reference wavelength

In equation \@ref(eq:cdom2), the reference wavelength was set at 350 nm. One question can potentially come to your mind. What is the effect of choosing a different reference wavelengths? What will append to $S$ if we change the reference wavelength to let's say 250? 

Fig. \@ref(fig:refwl) shows that:

- Little effect (computational rounding)

```{r refwl, echo=FALSE, fig.cap="Effect of varying the reference wavelength on S."}

ref_wl <- seq(250, 400, by = 5)

mods <- lapply(ref_wl, function(x) {
  f <- substitute(spc1 ~ a0 * exp(-s * (wavelength - x)) + k, list(x = x))
  
  nls(f, data = spectra, start = list(a0 = 5, s = 0.02, k = 0))
  
})

coefs <- lapply(mods, coef) 
coefs <- as.data.frame(do.call(rbind, coefs)) %>% 
  mutate(wavelength = ref_wl) 

p <- coefs %>% 
  ggplot(aes(x = wavelength, y = s)) +
  geom_line() +
  geom_point() +
  xlab("Wavelength (nm)") +
  ylab(bquote(S~(nm^{-1})))

p
```

- Plot the calculated curves on a graph

#### Choice of the spectral range

- @Massicotte2016MC

## Metrics

- $S_{300-600}$ linked to DOM molecular weight [@Stedmon2015b].

### Slope ratio

Equation \@ref(eq:sr) shows how the slope ratio ($S_R$) is calculated.

\begin{equation}
S_R = \frac{S_{275-295}}{S_{350-400}}
\label{eq:sr}
\end{equation}

> By calculating the ratio of the slope of the shorter wavelength region (275–295 nm) to that of the longer wavelength region (350–400 nm), a dimensionless parameter called "slope ratio" or $S_R$ is defined. This approach avoids the use of spectral data near the detection limit of the instruments used, and focuses on absorbance values that shift dramatically during estuarine transit and photochemical alteration of CDOM [@Helms2008].

Figure \@ref(fig:sr) shows in red the 275-295 and 350-400 nm spectral range.

```{r sr, echo=FALSE, fig.cap="Spectral range used to calculate the slope ratio."}
df1 <- spectra %>%
  filter(wavelength %in% 275:295)

df2 <- spectra %>%
  filter(wavelength %in% 350:400)

p +
  geom_line(data = df1, aes(x = wavelength, y = spc1), col = "red") +
  geom_line(data = df2, aes(x = wavelength, y = spc1), col = "red")
```
