---
title: "Practical guide on dissolved organic matter (DOM) optic"
author: "Philippe Massicotte"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: /home/persican/Documents/library.bib
biblio-style: apalike
link-citations: yes
github-repo: PMassicotte/dom-optic
description: "A practical guide on dissolved organic matter optic."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library(extrafont)
library(tidyr)
library(eemR)
library(plot3D)

loadfonts(quiet = TRUE)
theme_set(theme_bw(base_size = 12, base_family = "Open Sans"))
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

# Introduction and motivations

Dissolved organic matter (DOM) plays a central role in the functioning of aquatic ecosystems. For example, characteristics of the DOM pool (quantity and quality) determine underwater light climate [@Kirk1994], the composition of aquatic microbial communities [@Foreman2003; @Kritzberg2006a] and the carbon cycling on local to global scales [@Cole2007]. Chemically, the DOM pool is complex (> 1500 compounds) and analytical methods used to characterize it are relatively complex, time-consuming and costly [@Benner2002; @Seitzinger2005; @Fellman2010]. This situation called for the development of rapid and cost effective characterization techniques. Because optical properties of DOM can be related to its chemical properties, optical techniques such as fluorescence spectroscopy have been developed and rapidly adopted by the community to characterize the DOM pool in aquatic ecosystems [@Coble1990; @Coble1996; @McKnight2001; @Fellman2008].

**This document aims at providing practical tools** that can serve as a starter to those who desire to start working with DOM. R code examples are also provided.

For those that are interested to learn in depth DOM biogeochemistry, there are excellent sources of fundamental information in the following books:

- @Lakowicz2006
- @Hansell2014
- @Findlay2003
- @Coble2014
